---
title: "On the move: A study on gait style and preference in early infancy"
author: "Sarah Shahriar & Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
    number_sections: true
    code_folding: hide
    self_contained: false
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(devtools)) {
  install.packages('devtools')
}
library(devtools)

if (!require(databraryapi)) {
  devtools::install_github('PLAY-behaviorome/databraryapi')
}
library(databraryapi)

if (!require(tidyverse)) {
  install.packages('tidyverse')
}
library(tidyverse)

if (!require(ggplot2)) {
  install.packages('ggplot2')
}
library(ggplot2)
```

# Purpose(s)

Evaluate 'mode' of crawling in PLAY project infants.

# Gather

## Define sample

12-mo-olds drawn from 

Adolph, K., Tamis-LeMonda, C. & Gilmore, R.O. (2017). PLAY Project: Pilot Data Collections. Databrary. Retrieved March 12, 2019 from https://nyu.databrary.org/volume/444#panel-data.

## Code data

### Code definitions

#### Crawling vs. other locomotion

Crawling is defined as locomotion in which the infant independently uses both right and left hands and knees with contact to the floor to move across a distance greater than 2 feet.

#### Hand onset

Hand onset is defined as the specific hand used to initiate hands-knees crawling.

### Contralateral vs. unilateral gait
Contralateral gait is defined as the usage of opposite hand and knee to move independently across a distance greater than 2 feet. Unilateral gait is defined as the usage of same-side hand and knee to move independently across a distance greater than 2 feet. 

### Coding procedure

1. Observe infant locomotion without inputs of coding initially.
2. Rewatch locomotion to observe unique hand initiation and crawling mode.
3. Collect specific onset and offset of infant locomotion.
4. Compile data for each participant and compare results between subjects.

## Acquire data & code data

1. Download session data (video and Datavyu files) from Databrary.
    - Participant 8: <https://nyu.databrary.org/volume/444/slot/18811/->
    - Participant 13: <https://nyu.databrary.org/volume/444/slot/18818/->
2. Examine each instance of locomotion using Datavyu file, code == 'l'.
3. Utilize Datavyu to collect the total time each participant spent using a specific mode of crawling.

### Export from Datavyu

The Datavyu (`.opf`) files are located in `~/Box\ Sync/b-gilmore-lab-group\ Shared/gilmore-lab/pubs/psi-chi/2019/crawl-type/`.

Let's list them.

```{r}
data_dir <- '~/Box\ Sync/b-gilmore-lab-group\ Shared/gilmore-lab/pubs/psi-chi/2019/crawl-type/'

dv_fl <- list.files(data_dir, pattern = '\\.opf$', full.names = TRUE)
dv_fl
```

Extract into subject-specific directories, e.g., `/13`, etc.

```{r}
# Extract sub number and reformat
subs <- stringr::str_match(dv_fl, pattern = '\\.S([0-9]+)\\.')[,2]
subs <- stringr::str_pad(subs, 2, pad='0')

extract_dv(in_dir = data_dir, in_fn = dv_fl[1], out_dir = paste0('crawling-mode_data/', subs[1]))
extract_dv(in_dir = data_dir, in_fn = dv_fl[2], out_dir = paste0('crawling-mode_data/', subs[2]))
extract_dv(in_dir = data_dir, in_fn = dv_fl[3], out_dir = paste0('crawling-mode_data/', subs[3]))
```

Convert the Datavyu files to CSVs.

```{r}
s13_csv <- dv_to_csv(dv_dir = 'crawling-mode_data/13', vb = TRUE)
s08_csv <- dv_to_csv(dv_dir = 'crawling-mode_data/08', vb = TRUE)
s20_csv <- dv_to_csv(dv_dir = 'crawling-mode_data/20', vb = TRUE)
```

Now we can read the Datavyu files as data frames.

s13 did not crawl, so using s20 instead.

```{r}
library(tidyverse)
s20 <- read_csv(s20_csv)
s08 <- read_csv(s08_csv)

s20$ID <- 20
s08$ID <- 08

crawl_init <- rbind(s20, s08)
```

# Clean

## Add duration field

```{r}
crawl_init <- crawl_init %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0)
```

## Select relevant codes

Select code `c`.

## Visualize `R_Initiation` and `L_Initiation` episode data

```{r}
code_r <- crawl_init %>% 
  filter(code == 'R_Initiation', code.value == 'c')
```

```{r}
code_l <- crawl_init %>% 
  filter(code == 'L_Initiation', code.value == 'c')
```

Combine `R_Initiation` and `L_Initiation` into single field.

```{r}
crawl_init <- crawl_init %>% 
  filter(code %in% c('R_Initiation', 'L_Initiation')) %>%
  rename(hand = code) %>%
  select(ID, hand, onset, offset, duration)

crawl_init$hand <- stringr::str_sub(crawl_init$hand, 1, 1)
```

# Visualize

```{r}
my_theme <- theme(axis.text.x = element_text(size = rel(1.5)),
                  axis.text.y = element_text(size = rel(1.5)),
                  plot.title = element_text(size = rel(3)),
                  axis.title = element_text(size = rel(2)),
                  legend.text = element_text(size = rel(2)),
                  strip.text.x = element_text(size = rel(2))) +
  theme_classic()
```

```{r left-right-durations-hist}
crawl_init %>% 
  ggplot() +
  aes(x = hand, y = duration, color = as.factor(ID)) +
  geom_boxplot() +
  geom_point() +
  facet_grid(. ~ ID) +
  xlab('Bout initiation hand') +
  ylab('Bout duration (secs)') +
  my_theme +
  theme(legend.position = 'none')
```

Note that the figure(s) are located in `crawling-mode_files/figure-html/`.

```{r}
xtabs(formula = ~ hand + ID, data = crawl_init) %>%
  knitr::kable()
```

# Analyze

# Illustrations

<https://nyu.databrary.org/slot/18811/1283000,1294000/asset/85451/download?inline=true>

```{r}
source('R/write_video_clip_html.R')
source('R/url_from_segment.R')
```

## R hand initiation

```{r, results='asis'}
seg_index <- 1
url <- url_from_segment(code_r[seg_index,], 444, 18811, 85451)
write_video_clip_html(url)
```

## L hand initiation

```{r, results='asis'}
seg_index <- 1
url <- url_from_segment(code_l[seg_index,], 444, 18811, 85451)
write_video_clip_html(url)
```

