---
title: "Object play"
author: "Ashton Dluzneski, Sandy Rayes, Zhichun Zhao, & Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
    number_sections: true
    code_folding: hide
    self_contained: false
params:
  db_account: rogilmore@psu.edu
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(devtools)) {
  install.packages('devtools')
}
library(devtools)

if (!require(databraryapi)) {
  devtools::install_github('PLAY-behaviorome/databraryapi')
}
library(databraryapi)

if (!require(tidyverse)) {
  install.packages('tidyverse')
}
library(tidyverse)

if (!require(ggplot2)) {
  install.packages('ggplot2')
}
library(ggplot2)

source('R/write_video_clip_html.R')
source('R/url_from_segment.R')
```

We will define some common graph theme elements here.

```{r}
my_theme <- theme(axis.text.x = element_text(size = rel(1.5)),
                  axis.text.y = element_text(size = rel(1.5)),
                  plot.title = element_text(size = rel(3)),
                  axis.title = element_text(size = rel(2)),
                  legend.text = element_text(size = rel(2))) +
  theme_classic()
```

# Motivation

# Sample selection

12, 18, and 24-mo-olds drawn from 

Adolph, K., Tamis-LeMonda, C. & Gilmore, R.O. (2017). PLAY Project: Pilot Data Collections. Databrary. Retrieved March 12, 2019 from https://nyu.databrary.org/volume/444#panel-data.

# Code definitions

# Coding procedure

## Acquire data

1. Download session data (video and Datavyu files) from Databrary.

2. Process OPF files

# Examples

## Participant 13

<https://nyu.databrary.org/slot/18818/101800000,101929771/asset/85723/download?inline=true>

# Coding

## Code definitions

## Coding procedure

# Gather

## Export from Datavyu

The Datavyu (`.opf`) files are located in `~/Box\ Sync/b-gilmore-lab-group\ Shared/gilmore-lab/pubs/psi-chi/2019/grasp-stack`.

Let's list them.

```{r}
data_dir <- '~/Box\ Sync/b-gilmore-lab-group\ Shared/gilmore-lab/pubs/psi-chi/2019/grasp-stack'

dv_fl <- list.files(data_dir, pattern = '\\.opf$', full.names = TRUE)
dv_fl
```

Extract into subject-specific directories, e.g., `/13`, etc.

```{r}
# Extract sub number and reformat
subs <- stringr::str_match(dv_fl, pattern = '_s([0-9]+)')[,2]
subs <- stringr::str_pad(subs, 2, pad='0')

for (i in 1:length(subs)) {
  databraryapi::extract_dv(in_dir = data_dir, in_fn = dv_fl[i], 
             out_dir = paste0('object-play_data/', subs[i]))
}
```

Convert the Datavyu files to CSVs.

```{r}
fl <- list.files('object-play_data', full.names = TRUE)
csv_list <- unlist(lapply(fl, databraryapi::dv_to_csv))
```

Now we can read the Datavyu files as data frames.

```{r}
#csvs <- lapply(csv_list, read_csv)
s09 <- read_csv(csv_list[1])
s13 <- read_csv(csv_list[2])
s14 <- read_csv(csv_list[3])
s17 <- read_csv(csv_list[4])
s19 <- read_csv(csv_list[5])
s20 <- read_csv(csv_list[6])
```

Add duration field and subject fields.

```{r}
s09 <- s09 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's09')

s13 <- s13 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's13')

s14 <- s14 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's14')

s17 <- s17 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's17')

s19 <- s19 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's19')

s20 <- s20 %>%
  mutate(duration = lubridate::as.period(offset - onset, unit = 'sec')) %>%
  filter(duration > 0) %>%
  mutate(sub = 's20')
```

## Merge separate data files into one

```{r}
data_list <- list(s09, s13, s14, s17, s19, s20)
object_play <- Reduce(function(x,y) merge(x,y, all=TRUE), data_list)
object_play <- object_play %>%
  mutate(ID = as.numeric(stringr::str_sub(sub, 2,3))) %>%
  select(-sub)
```

## Import demographic data from Databrary

```{r}
login_db(params$db_account)
vol_444 <- databraryapi::download_session_csv(vol_id = 444)
sub_info <- vol_444 %>%
  filter(participant.ID %in% as.numeric(subs)) %>%
  select(session_id, participant.ID, participant.gender, participant.race, 
         participant.ethnicity, participant.gestational.age, 
         participant.birth.weight, group.name) %>%
  rename(ID = participant.ID, 
         gender = participant.gender, race = participant.race,
         ethnicity = participant.ethnicity, 
         gest_age = participant.gestational.age, 
         birth_weight = participant.birth.weight, 
         age_group = group.name)
```

# Cleaning

## Select relevant codes

List the unique codes.

```{r}
unique(object_play$code)
```

There are three types of codes, `r unique(object_play$code)[1]`, `r unique(object_play$code)[2]`, and `r unique(object_play$code)[3]`.

## Merge demographic data with coded data

```{r}
object_merged <- dplyr::left_join(object_play, sub_info, by = c('ID'))
```

## Get video asset_ids for selected sessions

If we want to show video excerpts, we need to access the raw videos within each participant session.

```{r}
# (videos_list <- databraryapi::list_assets_in_session(vol_id = 444, session_id = sub_info[1,]$session_id))
# 
# # Select video with '1-Hour' in name field?
# vid <- videos_list %>% 
#   filter(stringr::str_detect(name, '1\\-Hour'))
# 
# No, because in pilot, this name is sometimes in the experimenter view video, too.
# observation.mp4, phone_quest.mp4, home_quest.mp4, dyadic.mp4, house_map.mp4 as better names?
# For this example, I may have to choose asset_id s manually.

vol_ids <- rep(444, n=6)
asset_ids <- c(85471, 85705, 85730, 85812, 85853, 85875)
session_ids <- sub_info['session_id']

make_session_urls <- function(vol_id, session_id, asset_id) {
  paste0('https://nyu.databrary.org/slot/', session_id, '/-/asset/', asset_id, '/download?inline=true')
}

for (i in 1:6) {
  make_session_urls(vol_ids[i], session_ids$session_id[i], asset_ids[i])
}
```

# Visualize

## Graphs & tables

### `hand_touch` code

```{r hand-touch-which-hand}
object_merged %>% 
  filter(code == 'hand_touch') %>%
  ggplot() +
  aes(x = code.value, y = duration, color = age_group) +
  geom_boxplot() +
  geom_point() +
  facet_wrap(ID ~ .) +
  xlab('Grasp type') +
  ylab('Duration (secs)') +
  my_theme
```

```{r}
d <- object_merged %>%
  filter(code == 'hand_touch')
xtabs(formula = ~ code.value + ID, data = d) %>%
  knitr::kable()
```

### `touch_throw` code

```{r touch-throw-which-hand}
object_merged %>% 
  filter(code == 'touch_throw') %>%
  ggplot() +
  aes(x = code.value, y = duration, color = age_group) +
  geom_boxplot() +
  geom_point() +
  facet_wrap(ID ~ .) +
  xlab('Grasp type') +
  ylab('Duration (secs)') +
  my_theme
```

```{r}
d <- object_merged %>%
  filter(code == 'touch_throw')
xtabs(formula = ~ code.value + ID, data = d) %>%
  knitr::kable()
```


```{r code-durations-boxplot}
object_merged %>% 
  ggplot() +
  aes(x = code, y = duration, color = age_group, shape = gender) +
  geom_boxplot() +
  geom_point() +
  facet_wrap(ID ~ .) +
  xlab('Behavior type') +
  ylab('Duration (secs)') +
  my_theme
```

```{r}
xtabs(formula = ~ code + ID, data = object_play) %>%
  knitr::kable()
```

Note that the figure(s) are located in `object-play_files/figure-html/`.

## Links to raw videos

**Note**: These links will open only for authorized Databrary investigators or affiliates who have permission to access the relevant files.
They are provided here for transparency.

### Participant `r sub_info[1,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[1], session_ids$session_id[1], asset_ids[1])
write_video_clip_html(url)
```

### Participant `r sub_info[2,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[2], session_ids$session_id[2], asset_ids[2])
write_video_clip_html(url)
```

### Participant `r sub_info[3,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[3], session_ids$session_id[3], asset_ids[3])
write_video_clip_html(url)
```

### Participant `r sub_info[4,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[4], session_ids$session_id[4], asset_ids[4])
write_video_clip_html(url)
```

### Participant `r sub_info[5,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[5], session_ids$session_id[5], asset_ids[5])
write_video_clip_html(url)
```

### Participant `r sub_info[6,'ID']`

```{r, results='asis'}
url <- make_session_urls(vol_ids[6], session_ids$session_id[6], asset_ids[6])
write_video_clip_html(url)
```
