---
title: "play-pilot-summary"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
    number_sections: true
    code_folding: hide
params: 
  db_account: rogilmore@psu.edu
---

# Purpose

This document summarizes the analyses conducted on the Play & Learning Across a Year (PLAY) project pilot data.
The data are stored and shared at <https://nyu.databrary.org/volume/444>.

# Set-up

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# Load databraryapi package from github.com/PLAY-behaviorome/databraryapi
if (!require(databraryapi)) {
  devtools::install_github("PLAY-behaviorome/databraryapi")
  library(databraryapi)
}

# Load other libraries
library(tidyverse)
library(ggplot2)

## Variables for this particular volume and session.
play_vol_id <- 444
survey_data_session_name = "Parent report data"
```

The Databrary volume is 444.

We need to log in to Databrary to have access to these data.
If you have logged-in before from the machine you are running this report, then you will be prompted to enter your Databrary ID (email address).
If you have *not* logged-in before, you will be prompted to enter your Databrary ID (email address) and your Databrary password.

```{r login}
databraryapi::login_db(params$db_account)
```

# Gather data

There are several data sources we need to gather and clean.
Participant demographic data are stored in the Databrary spreadsheet.
Parent report (survey) data are stored in the session with `session_name` == "Parent report data".
Let's store that in a variable for later use: `r 

## Participant demographics

We'll first gather the participant demographic data stored in the Databrary spreadsheet.

```{r gather-participant-demographic-data}
play_demog_raw <- databraryapi::download_session_csv(vol_id = play_vol_id)

if (is.null(play_demog_raw)) {
  stop("No data downloaded from Databrary. Are you logged in?")
}

# Select relevant spreadsheet columns, filter those with actual session data, and rename variables to use underscores
play_demog <- play_demog_raw %>%
  select(session_id, session_release, participant.gender,
         participant.race, participant.ethnicity,
         participant.gestational.age, participant.birth.weight,
         participant.disability, participant.language, group.name,
         context.language) %>%
  filter(session_release %in% c('EXCERPTS', 'PRIVATE', 'SHARED')) %>%
  rename(participant_gender = participant.gender,
         participant_race = participant.race,
         participant_ethnicity = participant.ethnicity,
         participant_gestational_age = participant.gestational.age,
         participant_birth_weight = participant.birth.weight,
         participant_disability = participant.disability, 
         participant_language = participant.language, 
         group_name = group.name,
         context_language = context.language)
```

### Structure of demographic data file

```{r}
str(play_demog)
```

## Parent report data

First, we need to list the data files available in the session where the parent report data are stored.

```{r}
parent_rpt_session_id <- play_demog_raw %>%
  filter(session_name == survey_data_session_name) %>%
  select(session_id) %>%
  as.numeric()
```

Now, we list the data files in that session.

```{r}
surveys <- list_assets_in_session(vol_id = play_vol_id,
                                  session_id = parent_rpt_session_id) %>%
  select(asset_id, name)
knitr::kable(surveys)
```

Let's download each of these separately.

```{r}
childcare_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, 
                               asset_id = surveys$asset_id[1])
loco_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, asset_id = surveys$asset_id[2])
childbirth_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, 
                                 asset_id = surveys$asset_id[3])
family_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, 
                                 asset_id = surveys$asset_id[4])
sleep_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, 
                                 asset_id = surveys$asset_id[5])
lang_exp_df <- read_csv_data_as_df(session_id = parent_rpt_session_id, 
                                 asset_id = surveys$asset_id[6])
```

### Examining structure of parent report data files

#### Locomotor milestones

```{r}
str(loco_df)
```

#### Childbirth and health

```{r}
str(childbirth_df)
```

#### Family structure

```{r}
str(family_df)
```

#### Sleep hygiene

```{r}
str(sleep_df)
```

#### Childcare arrangements

```{r}
str(childcare_df)
```

#### Language exposure

```{r}
str(lang_exp_df)
```

# Plot data

Let's set some plot thematic elements.

```{r}
play.palette <- scale_fill_manual(values=c("blue2", "firebrick2", "chartreuse2", "darkorchid2"))
play.theme <-   
  theme_classic() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = rel(1.2)),
        axis.title = element_text(size = rel(1.5), face ="bold"),
        axis.text.x = element_text(size = rel(1.2)),
        axis.text.y = element_text(size = rel(1.2)),
        axis.line = element_blank(),
        axis.title.y = element_blank())
```

## Participant demographics

```{r}
play_demog %>% 
  ggplot(.) +
  aes(x = participant_gestational_age, y = participant_birth_weight, color = participant_race) +
  geom_point()
```

## Parent surveys

These are some illustrative plots.

### Language exposure

```{r}
lang_exp_df %>%
  ggplot(.) +
  aes(x = language) +
  facet_grid(exposure_context ~ .) +
  geom_histogram(stat='count') +
  play.theme
```

### Locomotion onset

```{r}
loco_df %>%
  gather(key = milestone, value = age.mos, 
         hkcrawl_onset_mos, walk_onset_mos) %>%
  mutate(milestone = factor(milestone, 
                            labels = c("crawl", "walk"))) %>%
  # arrange(desc(age.mos)) %>%
  ggplot() +
  aes(x = age.mos, y = id) +
  geom_point(aes(shape = milestone, color = milestone)) +
  geom_line(aes(group = id)) +
  xlab("Age (months)") +
  ylab("Participant ID") +
  geom_rug(aes(x = age.mos, group = milestone, color = milestone),
           sides = "b") +
  play.theme
```

