---
title: "walk-sleep"
author: "Michelle Mendez & Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_levels: 3
    toc_float: true
    number_sections: true
    code_folding: hide
    self_contained: false
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(devtools)) {
  install.packages('devtools')
}
library(devtools)

if (!require(databraryapi)) {
  devtools::install_github('PLAY-behaviorome/databraryapi')
}
library(databraryapi)

if (!require(tidyverse)) {
  install.packages('tidyverse')
}
library(tidyverse)

if (!require(ggplot2)) {
  install.packages('ggplot2')
}
library(ggplot2)
```

# Purpose

Using the PLAY project pilot data, compare a child’s sleeping patterns with the age they began crawling and walking and their method of childcare.

To see if there is a correlation between number of hours of sleep a child gets at night, their method of childcare and the amount of time they went from crawling to walking

# Gather

Import data from a csv file stored in `walk-sleep_data/`.

```{r}
data_dir <- 'walk-sleep_data/'
walk_sleep <- read_csv('walk-sleep_data/walk-sleep.csv')
```

# Clean

We need to make sure that `crawl_mos`, and `sleep_hrs` are numbers.

```{r}
walk_sleep$crawl_mos <- as.numeric(walk_sleep$crawl_mos)
walk_sleep$sleep_hrs <- lubridate::hms(walk_sleep$sleep_hrs)
```

# Visualize

We will define some common graph theme elements here.

```{r}
my_theme <- theme(axis.text.x = element_text(size = rel(1.5)),
                  axis.text.y = element_text(size = rel(1.5)),
                  plot.title = element_text(size = rel(3)),
                  axis.title = element_text(size = rel(2)),
                  legend.text = element_text(size = rel(2))) +
  theme_classic()
```

Hours of night sleep by age at walk onset.

```{r walk-onset-sleep-hrs}
walk_sleep %>%
  ggplot() +
  aes(x = walk_mos, y = as.numeric(sleep_hrs, "hours")) +
  geom_point() +
  geom_smooth(method='lm', formula = y ~ x) +
  xlab('Walking onset (mos)') +
  ylab('Night sleep (hrs)') +
  my_theme
```

Let's also look at the total time spent crawling as a predictor.
We'll define a new variable, `mos_crawling` to do this.

```{r}
walk_sleep <- walk_sleep %>%
  mutate(mos_crawling = walk_mos - crawl_mos)
walk_sleep
```

We don't have data for all participants here, so the sample is smaller.

```{r mos-crawling-sleep-hrs}
walk_sleep %>%
  ggplot() +
  aes(x = mos_crawling, y = as.numeric(sleep_hrs, "hours")) +
  geom_point() +
  geom_smooth(method='lm', formula = y ~ x) +
  xlab('Months spent crawling') +
  ylab('Night sleep (hrs)') +
  my_theme
```

```{r sleep-childcare}
walk_sleep %>%
  ggplot() +
  aes(x = as.numeric(sleep_hrs, "hours"), fill = childcare) +
  geom_histogram(bins = 7) +
  xlab('Night sleep (hrs)') +
  my_theme +
  theme(legend.position = 'bottom')
```

# Analyze

We test the association between `sleep_hrs` and `walk_mos` with a Pearson's product-moment correlation.

```{r}
c <- with(walk_sleep, cor.test(as.numeric(sleep_hrs), walk_mos))
c
```

We find that there is a correlation of $r$=`r c$estimate` but the 95% confidence interval of [`r c$conf.int[1]`, `r c$conf.int[2]`] includes 0, so we cannot infer a relationship.

We also fit a linear regression line to these data.
The `sleep_hrs` variable must be made numeric before we do so.

```{r}
lr <- lm(formula = as.numeric(sleep_hrs) ~ walk_mos, data = walk_sleep)
summary(lr)
```

Again, there is an expected non-zero value for the intercept, but no statistically signficant relationship between `sleep_hrs` and `walk_mos`.
